%-------------------------
% Resume in Latex
% Original Author: Sourabh Bajaj
% Original Repository: https://github.com/sb2nov/resume
% Adaptation: Waqas Ali
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeEducationSubheading}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://waqasali.dev/}{\Large Waqas Ali}} &  \href{mailto:waqas.abbasi@outlook.com}{waqas.abbasi@outlook.com}\\
  \href{https://waqasali.dev/}{https://waqasali.dev} & \href{tel:+85259867711}{+852 5986 7711}\\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeEducationSubheading
      {The University of Hong Kong}{}
      {Bachelor of Engineering in Computer Science (Minor in Cognitive Science)}{Sept. 2016 -- May 2020}{Full Scholarship}{GPA: 3.51/4.30}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Credit Suisse}{Hong Kong}
      {Software Engineer}{August 2020 - Current}
      \resumeItemListStart
        \resumeItem{Private Banking}
          {Matched investment ideas with preferences and regulatory requirements of thousands of clients on one screen. Allowed planning, review, preview, and send-off of emails, SMSs, and push notifications. Created on-brand interfaces with advanced filtering and data sourcing using React, Styled Components, and Typescript. Used Node.js \& MongoDB for the GraphQL API.}
        \resumeItem{Campaign Analytics}
          {Developed a system to track conversions of the above-mentioned campaigns. Developed performant visualizations using vanilla CSS, virtualized tables, unit-tested filters, and processed data using Clojure in an ETL pipeline.}
        \resumeItem{Gitlab1s}
          {Ported the open-source \href{http://github1s.com}{github1s.com} project internally to allow a quick preview of internal repositories across the APAC region.}
        \resumeItem{Data Pipeline}
          {Implemented horizontal auto-scaling by migrating from virtual machines to Kubernetes using GitOps for transparent and self-documenting cluster management. Dockerized Kotlin apps, deployed Kafka/ZooKeeper/Kafka Connect, and implemented push-based health monitoring using Kotlin.}
      \resumeItemListEnd
      
    \resumeSubSubheading
      {Software Engineer, Intern}{June - August 2019}
      \resumeItemListStart
        \resumeItem{Client Recommendation}
          {Developed an idea recommendation platform powered by a content-based machine learning model with TypeScript, GraphQL, React, and OAuth. Used CSS and Recharts for several visualizations. Implemented continuous integration and deployment using GitLab CI, Docker, and Kubernetes.}
        \resumeItem{CodeIT Suisse}
        {Developed a programming competition platform for a recruitment event using Java, Spring Boot, and Vue. Added badges for gamification, performance graphs, admin dashboard, real-time grading, and BDD testing using Cucumber.}
    \resumeItemListEnd

    \resumeSubheading
      {GRAIL Inc.}{Hong Kong; Menlo Park, CA, USA}
      {Full Stack Software Engineer, Intern}{June - August 2018}
      \resumeItemListStart
        \resumeItem{Removed the need for manual invoicing every month}
          {by implementing an auto-invoicing system. Auto-generated PDFs for each invoice and integrated with NetSuite and Salesforce to sync customer information in real-time. Developed a dashboard for company finances. Used React, Material UI, Redux, Go, and SQL. Added several unit and integration tests.}
        \resumeItem{Allowed billing flexibility}
          {by adding features for invoice correction, discount offerings, and special pricing per customer. Worked on both front-end and back-end.}
      \resumeItemListEnd

    \resumeSubheading
      {Microsoft}{Hong Kong}
      {Technology Solutions Professional, Intern}{June - August 2017}
      \resumeItemListStart
        \resumeItem{Reduced time for sales to find Azure offerings for clients}
          {through a web app that allowed convenient searching and filtering of offered products with comparisons to competitors such as AWS.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Acumen}
      {Final Year Project: A distributed system to improve latency, efficiency, and throughput of machine learning inference pipelines. Used TensorFlow, gRPC, Docker, and Node.js. Paper at \href{https://github.com/WaqasAliAbbasi/HKU-FYP/blob/master/documents/FinalReport/FinalReport.pdf}{github.com/WaqasAliAbbasi/HKU-FYP}}
    \resumeSubItem{DragonSearch}
      {Academic search engine powered by ElasticSearch that helps filter through millions of papers, authors, and topics by asking for real-time user feedback. - Winner of Chengdu80 2019 inter-university FinTech competition}
    \resumeSubItem{StudentBase}
      {High school community with 10,000 monthly active users (\href{https://studentbase.app}{https://studentbase.app}). Infrastructure as Code (Terraform), CI/CD, GraphQL Server with 90\% testing coverage, S3 for content storage, Dockerized, React/Node.js/TypeScript, SSR using Next.js, Seed-funded HK\$100,000 by Hong Kong Science Park.}
    
  \resumeSubHeadingListEnd

\section{Skills \& Additional Experience}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Typescript, CSS, SQL, Clojure, Java, Haskell, Go, Python, Kotlin}
    \resumeSubItem{Tools/Frameworks}
      {React, Figma, Material UI, Tailwind CSS, GraphQL, Kubernetes, Django, gRPC}
    \resumeSubItem{Teaching Assistant}
      {ENGG1111 - Computer Programming and Applications}
 \resumeSubHeadingListEnd

\end{document}